Tor's Usability for Censorship Circumvention

### 2016-04-06 pets2017-paper/pets2017-paper.tex
Fix typo and note TODO

This mistake can results in users struggling through the rest of the interface similarly to those in the intermediate and advanced censorship environments. Participants in the intermediate and advanced censorship environments who did correctly choose to configure in intermediate did not actively display an understanding between the difference between censorship of websites versus censorship of the Tor relays.

>>>>

This mistake can result in users struggling through the rest of the interface similarly to those in the intermediate and advanced censorship environments.
% FIXME:
Participants in the intermediate and advanced censorship environments who did correctly choose to configure in intermediate did not actively display an understanding between the difference between censorship of websites versus censorship of the Tor relays.
